Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-30 bbbq_article.tex
Fix refs

Plotting the normalized values of presented TMH-derived epitopes (where
$1.0$ denotes that the percentage of presented TMH-derived epitopes
matches the values as expected by chance) in \ref{fig:rel_presentation}
shows that MHC-II has a higher relative over-presentation of TMH-derived
epitopes, when compared to MHC-I. \richel{HIERO}
The MHC-I molecule presents epitopes of shorter length than MHC-II.
We expect this to be of no influence in the presentation level
of TMH-derived epitopes, for each of the three proteomes.
We verified this, by normalizing the percentage of TMH-derived epitopes found
to the percentage of TMH-derived epitopes expected, 
where a value of $1.0$ denotes that the percentage of TMH-derived epitopes found
matches the percentage as expected by chance.
\richel{TODO: explain only the results found. Elaborate. Draw a conclusion}
Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
\richel{Add exact method}
See \ref{fig:rel_presentation} and \ref{fig:rel_presentation_per_haplotype}.

@@

There have been more efforts to look at the conservation of TMHs,
using different methodologies.
One such example is \ref{stevens2001substitution}, 
in which aligned protein sequence data was used.
Also this study found that TMHs are evolutionarily more conserved,
as the mean amino acid substitution rate in TMHs is about ten
percent lower,
which is the same value as this study found.
Another example is a study that estimates the conservation
scores for TMH and soluble regions based on 
evolutionary related protein alignments,
and found that TMHs are more conserved, 
with a conservation score that was 17\% higher in 
TMHs (\ref{oberai2009structural}).
Note that the last study also used human SNPs
and found that mutations in TMH are likelier to cause
a disease, again underlining the importance of TMHs.

>>>>

Plotting the normalized values of presented TMH-derived epitopes (where
$1.0$ denotes that the percentage of presented TMH-derived epitopes
matches the values as expected by chance) in \ref{fig:rel_presentation}
shows that MHC-II has a higher relative over-presentation of TMH-derived
epitopes, when compared to MHC-I.
The MHC-I molecule presents epitopes of shorter length than MHC-II.
We expect this to be of no influence in the presentation level
of TMH-derived epitopes, for each of the three proteomes.
We verified this, by normalizing the percentage of TMH-derived epitopes found
to the percentage of TMH-derived epitopes expected, 
where a value of $1.0$ denotes that the percentage of TMH-derived epitopes found
matches the percentage as expected by chance.
\richel{TODO: explain only the results found. Elaborate. Draw a conclusion}
Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
\richel{Add exact method}
See \ref{fig:rel_presentation} and \ref{fig:rel_presentation_per_haplotype}.

@@

There have been more efforts to look at the conservation of TMHs,
using different methodologies.
One such example is \cite{stevens2001substitution}, 
in which aligned protein sequence data was used.
Also this study found that TMHs are evolutionarily more conserved,
as the mean amino acid substitution rate in TMHs is about ten
percent lower,
which is the same value as this study found.
Another example is a study that estimates the conservation
scores for TMH and soluble regions based on 
evolutionary related protein alignments,
and found that TMHs are more conserved, 
with a conservation score that was 17\% higher in 
TMHs (\cite{oberai2009structural}).
Note that the last study also used human SNPs
and found that mutations in TMH are likelier to cause
a disease, again underlining the importance of TMHs.
